**install packages Dplyr**

```{r}
library(tidyverse)
library(dplyr)

```

```{r}
y3=letters[-1:-21]
y3
```

**create sample data**

data frame function used to create data

```{r}
my_data<-data.frame(y1=c(1:5),y2=letters[-1:-21],y3=5:1)
my_data

```

**Creating the new variable**

^variable name jothi_y1 created , the vakues from addition of variables y1 and y3 the mutate function used.^

```{r}
new_data <- my_data %>%  mutate(jothi_y1=y1+y3)
new_data   # print sample data

```

**Rename the variable / column name**

variable name y1 rename as sabai_y1 using renaming function

```{r}
new_data %>% rename(sabai_y1=y1)
```

**Selecting the specific variables by our choice\_ select function used,**

selecting the variable names y1,jothi\_\_1 and y2

```{r}
new_data %>% select(y1,jothi_y1,y2)
```

**Arrange** function used to rearrange the values of the variables

variable y1 values are manipulate in to descending orders

```{r}
new_data %>% arrange(desc(y1)) # descending order

```

variable y1 values are manipulate in to descending orders

```{r}
new_data %>% arrange(y1)  # ascending order
```

**Order function** Alternate method for sorting ascending to the variable values

```{r}
new_data[order(new_data$y2),]  

```

**Order function** Alternate method for sorting descending to the variable values

```{r}
new_data[rev(order(new_data$y2)),]

```

**SLICE** \_ selecting the rows , slice function used to show requested number of rows.

i am calling here only 2 rows here.

```{r}
new_data %>% slice(1:2)
```

filtering the rows or values of the variables by conditions

filtering the value of y1 greater then 3, and y3 is less then 2

```{r}
new_data %>% filter(y1>3 & y3<2)


```

**summarize** the data by grouping

grouping the jothi_y1 variable and summarise it for mean, new variable mean_y1 created.

```{r}
new_data %>% group_by(jothi_y1) %>% summarise(mean_y1=mean(y1))
```

**counting** the rows by group

the number of times v ,w, .... occured shown in "n" column

```{r}
new_data %>% count(y2)
```
